---
title: "Lung_Digest"
author: "Mark Snyder"
date: "8/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Packages utilized in this analysis
```{r}
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(ggrepel)
library(scProportionTest)
library(EnhancedVolcano)
```


Loading rds
```{r}
pathway <- "/Users/MES374/Documents/2021_Digest/combined.lung.named.rds"
digest <- readRDS(pathway)
```
##See additional code for the pre-processing and creation of this rds
Explore data: 
head(digest@meta.data, 5)
DimPlot(digest, reduction = "umap")
DimPlot(digest, reduction = "umap", group.by = "hash.ID")


Assigning protocol based on HTO
```{r}
digest$cat <- plyr::mapvalues(
  x = digest$hash.ID, 
  from = c("HTO-1-lung4", "HTO-2-lung4", "HTO-3-lung4", "HTO-5-lung4", "HTO-3-lung", "Negative"), 
  to = c("Protocol_A", "Protocol_A", "Protocol_A", "Protocol_A", "Protocol_B", "Protocol_B")
)
```

Testing population proportion based on protocol
```{r}
digest$CellType <- Idents(digest)

prop_test <- sc_utils(digest)

prop_test <- permutation_test(
  prop_test, cluster_identity = "CellType",
  sample_1 = "immune cell enriched", sample_2 = "epithelial cell enriched",
  sample_identity = "lung.ident"
)

permutation_plot(prop_test)
```


Subsetting T cells
```{r}
#Subset T cells
digest_CD3 <- subset(digest, subset = CD8A > 0.5)
digest_CD3 <- subset(digest_CD3, subset = LYZ < 0.5)
digest_CD3 <- subset(digest_CD3, subset = SFTPC < 2)
digest_CD3 <- subset(digest_CD3, subset = HBB < 0.8)

Idents(digest_CD3) <- "lung.ident"
```


Volcano Plot for T cells
```{r}
dig.response <- FindMarkers(digest_CD3, ident.1 = "immune cell enriched", ident.2 = "epithelial cell enriched", verbose = FALSE)

EnhancedVolcano(dig.response , 
                rownames(dig.response),
                x ="avg_log2FC", 
                y ="p_val_adj", 
                xlim = c(-2, 2),
                ylim = c(0,15),
                FCcutoff = 0.8,
                title = "T cell subset", 
                subtitle = "Protocol 5 vs 3")

```


Subset Myeloid cells
```{r}
#Subset Myeloid
digest_M <- subset(digest, subset = LYZ > 0.5)
digest_M <- subset(digest_M, subset = CD68 > 0.5)
digest_M <- subset(digest_M, subset = CD8A < 2)
digest_M <- subset(digest_M, subset = CD3E < 2)
digest_M <- subset(digest_M, subset = HBB < 0.8)
digest_M <- subset(digest_M, subset = SFTPC < 0.8)

Idents(digest_M) <- "lung.ident"
```


Myeloid Volcano Plot
```{r}
digM.response <- FindMarkers(digest_M, ident.1 = "immune cell enriched", ident.2 = "epithelial cell enriched", verbose = FALSE)


EnhancedVolcano(digM.response , 
                rownames(digM.response),
                x ="avg_log2FC", 
                y ="p_val_adj", 
                xlim = c(-2, 2),
                ylim = c(0,30),
                FCcutoff = 0.8,
                title = "Myeloid Subset", 
                subtitle = "Protocol 5 vs 3")
```


